Millions of Type Errors

### 2023-09-11 programming23/paper.tex
Getting LaTeX to run without error
Can't use greater-than as a filename char

\usepackage{alltt}
\usepackage[backend=biber]{biblatex}
\usepackage{amssymb}
\usepackage{calc}
\usepackage{colortbl}
\usepackage{listings}
\usepackage{mathpartir}
\usepackage{pifont}
\usepackage{siunitx}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{wasysym}
\usepackage{xcolor}
\usetikzlibrary{shapes.geometric}

@@

  \includegraphics[width=\columnwidth]{img/error-count-nocheck-row->te-density-diff.pdf}
  \includegraphics[width=\columnwidth]{img/error-count-nonstrict-row->te-density-diff.pdf}
  \includegraphics[width=\columnwidth]{img/error-count-strict-row->te-density-diff.pdf}

@@

\begin{figure}[t]\centering
  %% TODO
  %% - thin bars
  %% - colors for good , bad (disagree) , neutral
  \begin{tabular}{lll}
    \mnocheck{} & \mnonstrict{} & \mstrict{} \\
    \includegraphics[width=0.3\columnwidth]{img/compass-nocheck.pdf}
    &
    \includegraphics[width=0.3\columnwidth]{img/compass-nonstrict.pdf}
    &
    \includegraphics[width=0.3\columnwidth]{img/compass-strict.pdf}
  \end{tabular}
  \caption{FILL Are there fewer type errors than forcedstrict errors? Expect true always, but that is not the case.}
  \label{f:tefs}
\end{figure}

>>>>

\usepackage{alltt}
\usepackage[backend=biber]{biblatex}
\usepackage{amssymb}
\usepackage{calc}
\usepackage{colortbl}
\usepackage{listings}
\usepackage{mathpartir}
\usepackage{pifont}
% Errors with
% ! Undefined control sequence.
% <argument> \l__siunitx_number_implicit_plus_bool 
% l.61 \begin{document}
% using Mac TeXlive 20230313_2
% \usepackage{siunitx}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{wasysym}
\usepackage{xcolor}
\usetikzlibrary{shapes.geometric}

@@

  % > is not a valid filename char on some OSs!
  \includegraphics[width=\columnwidth]{img/error-count-nocheck-row--te-density-diff.pdf}
  \includegraphics[width=\columnwidth]{img/error-count-nonstrict-row--te-density-diff.pdf}
  \includegraphics[width=\columnwidth]{img/error-count-strict-row--te-density-diff.pdf}

@@

\begin{figure}[t]\centering
  %% TODO
  %% - thin bars
  %% - colors for good , bad (disagree) , neutral
  \begin{tabular}{lll}
    \mnocheck{} & \mnonstrict{} & \mstrict{} \\
    % Missing file
    % \includegraphics[width=0.3\columnwidth]{img/compass-nocheck.pdf}
    &
    % Missing file
    % \includegraphics[width=0.3\columnwidth]{img/compass-nonstrict.pdf}
    &
    % Missing file
    % \includegraphics[width=0.3\columnwidth]{img/compass-strict.pdf}
  \end{tabular}
  \caption{FILL Are there fewer type errors than forcedstrict errors? Expect true always, but that is not the case.}
  \label{f:tefs}
\end{figure}
